---
title: "<i class=bi-arrow-repeat style=font-size:1em></i>&nbsp;Præmier & deltagere"
subtitle: "DM i Ping Pong {{< var var.afholdelsesår >}}<br><i class=small> {{< var var.afholdelsesdag >}} i [{{< var var.lokation_sted >}}]({{< var var.lokation_link >}}){target=_blank}</i>"
editor_options:
  chunk_output_type: console
---

```{r}
source(file = "input_dm_ping_pong.R", local = knitr::knit_global())
```

`r tbl0_stat$k_status_cta_plakat`

`r tbl0_stat$k_sidst_opdateret`

## Præmier

```{r}
kbl1_præmier_penge
kbl1_præmier_yngst_ældst
```

## Deltagere

`r paste0("<i style=font-size:80%>", tbl0_stat$k_billetantal_billettype, "<br>", tbl0_stat$k_klubantal, "<br>", tbl0_stat$k_deltagerantal_gentilmelding, "<br>", tbl0_stat$k_deltagerantal_køn, "<br>", tbl0_stat$k_deltagerantal_aldersgruppe, "<br>", tbl0_stat$k_alder, "</i>")`

```{r}
if(tbl0_input$k_status_1_2_3_4 == 3) { kbl2_deltagere_foreløbig }

if(tbl0_input$k_status_1_2_3_4 == 1 | tbl0_input$k_status_1_2_3_4 == 2 | tbl0_input$k_status_1_2_3_4 == 4) { kbl2_deltagere_puljer }

if(tbl0_input$k_status_1_2_3_4 == 1 | tbl0_input$k_status_1_2_3_4 == 2 | tbl0_input$k_status_1_2_3_4 == 4) { kbl2_deltagere_fest }
```

## Dashboards

```{r}
#| fig-height: 2
#| layout-ncol: 2
graf1_tilmeldingstype
graf2_gentilmelding
```

```{r}
#| layout-ncol: 2
graf3_klubber
graf4_DK
```

`r paste0("<i style=font-size:80%>", tbl0_stat$k_deltagerantal_landsdel, "<br>", tbl0_stat$k_deltagerantal_region, "<br>", tbl0_stat$k_deltagerantal_ingen_klub, "</i>")`
